% Gameplay

\subsection{Game mechanics}

Throughout the following sections the main aspects of \game\ game mechanics will be
profusely discussed with the purpose of describing in an accurate way how
players will interact with the game.\\

% Armies & civilizations (bonuses)
\subsubsection{Armies and civilizations}

In every battle, the player will command an army from a given civilization based
on a concrete historical period no matter if it is a quick battle, a complete
campaign or an online encounter. Each player's army will be identified thanks
to its colour scheme which can be blue, red, green or yellow. The colour scheme
has nothing to do with the chosen civilization.\\

Each civilization will have access to a possibly different set of units. For
example, the S.XVIII Spanish navy might have a warship the French can't produce
and so on. On top of that, a given civilization may be specialized in some
kind of units so they have greater qualities (movement, attack or defense).\\

% Map
\subsubsection{Maps}

    % Victory objectives

Maps or battles (synonyms) are \game's base. When a player starts a map, two
armies will fight to obtain the victory. This goal can be achieved either by
killing all enemy units or by conquering the opponent's Operations center. Maps
will be tiled based, that is, they will be composed of a big mesh of squares.\\
 
    % Unit movement

Players will command their respective army during time limited turns. When it's
a player's turn, he can either move his units, command them to attack, conquer
enemy facilities or ask for reinforcements. When a unit is selected, a map
region will be highlighted showing the unit's reach for that turn. The distance
a given unit can walk in a turn will be determined by its properties and the
terrain it has to traverse. A unit that walks all its moving distance can still
attack the enemy in the same turn.\\

    % Unit attack

Player's units can attack the enemy if the second ones are within the attack
range of the first ones. It's important to mention that there are long
distance units (eg. artillery) and close combat units (eg. infantry). Although
melee units have to be in an adjacent position in the map in order to attack an
enemy, distance units reach the target from a longer distance. To attack, the
player has to select the attacking unit and every reachable enemy unit will be
highlighted, then the user has to select the objective and confirm the action.
When a unit attacks the enemy it becomes unavailable for the rest of the turn.\\

    % Territory control

Players will struggle to control more and more territory as the game evolves.
There will be several cities and facilities spread over the map and units can
take them. At the start of each turn, armies will receive certain quantity of
resources depending on how many buildings are under their control. To take a
city or facility, the player has to move a unit to the correspondent map
position and select the \emph{conquer} option.\\

    % Reinforcements

A commander can ask for reinforcements if his army has enough resources. To
gather new units the player must select a special building called barrack
(only if it's already conquered) and choose the desired unit type. Each unit
has a cost proportional to its power. A barrack can produce only one unit per
turn.\\

    % Vision

When a battle starts the map is covered with war fog which means that it's
possible to see the terrain type in each area but enemy units are hidden. The
player will only be able to see enemy units if they're within the vision range
of their own units. Vision range is a unit property, so different units may
have different vision ranges.\\


% User login & scoreboards
\subsubsection{User login and scoreboards}

\game\ will have a strong competitive component thanks to global scoreboards.
If the player wants to access this feature he will have to register with a
nickname, e-mail address and password from the game menu itself. When an
official campaign map ends, the user will receive a score, if he's logged on, the
game will submit it to a server. With this information is possible to check the
best 10 players in the whole world of \game.\\

If two registered players play in the online multiplayer mode the result will
be submitted to the server as well. Every player would be able to see their
performance in terms of victories, defeats and ratio victories/defeats among
the best players in the world scores.\\

% Campaign & difficulty
\subsubsection{Campaigns and difficulty}

Campaign mode in \game\ is composed of map groups tied together in linear
order so they recreate an historical conflict (eg. WWII). For scheduling
reasons, initially the game will only have one campaign available reasons but
the engine will support campaign creation.\\

As the player plays the maps in a campaign, difficulty will increase making
each battle more and more challenging. Difficulty must be carefully adjusted so
levels are not excessively inaccessible.\\


% Online multiplayer rules
\subsubsection{Online multiplayer rules}

\game\ will support online battles up to four players at the same time. One
player has to be the host while the rest will have a client role. The host must
select the online multiplayer match creation option while the rest will have to
join the room created by the host (entering the host IP). Although every player
can communicate with each other through a in-menu chat, the host will be the
only one able to select the map to fight.\\

Once the map starts, players will continue to be able to communicate through
the same chat system. Whenever a player leaves the game (by his own will or by
connection problems) the system will replace the lost commander with the AI.
Unfortunately, the player won't be able to join again. En every other way,
players will interact with the game as if it was a single player battle.\\

\subsection{Comprised historical period}

The official campaign initially distributed with \game\ will be based on World
War II (WWII from now on). Battles will be held in both front lines, the Pacific
and European ones. Every weapon, building and unit should accurately represent
the WWII set. However, the visual style doesn't require highly detailed
elements, just the opposite.\\

\subsection{Units}

% Infantry: light, heavy
% Vehicles: recon, tank, heavy tank, anti-air
% Artillery: artillery, rocket launcher, anti-air missiles
% Ground transport

The following table contains the names and properties of every ground unit in
\game.\\

\begin{table}[H]
    \label{tab:ground-units}
    \begin{center}
    \begin{tabular}{| l | m{1cm} | m{1.7cm} | m{1.0cm} | m{1.5cm} | m{1.1cm} | m{2.5cm} | m{2.5cm} |}
        \hline
        \textbf{Unit name} & \textbf{Cost} & \textbf{Movement} & \textbf{Power} & \textbf{Defense} & \textbf{Vision} & \textbf{Strengths} & \textbf{Weaknesses} \\
        \hline
        Light infantry &  &  &  &  &  &  &  \\
        \hline
        Heavy infantry &  &  &  &  &  &  &  \\
        \hline
        Recon &  &  &  &  &  &  &  \\
        \hline
        Tank &  &  &  &  &  &  &  \\
        \hline
        Heavy tank &  &  &  &  &  &  &  \\
        \hline
        Anti-air &  &  &  &  &  &  &  \\
        \hline
        Artillery &  &  &  &  &  &  &  \\
        \hline
        Rocket launcher &  &  &  &  &  &  &  \\
        \hline
        Transport &  &  &  &  &  &  &  \\
        \hline
    \end{tabular}
    \end{center}
\caption{Ground units and their properties}
\end{table}

\textbf{Additional restrictions}: Anti-air units can only attack air enemy
units and Transport units cannot attack at all.\\


% Sea: transport, submarine, cruiser, battleship

The table below contains the names and attributes of every sea unit in \game.\\

\begin{table}[H]
    \label{tab:sea-units}
    \begin{center}
    \begin{tabular}{| l | m{1cm} | m{1.7cm} | m{1.0cm} | m{1.5cm} | m{1.1cm} | m{2.5cm} | m{2.5cm} |}
        \hline
        \textbf{Unit name} & \textbf{Cost} & \textbf{Movement} & \textbf{Power} & \textbf{Defense} & \textbf{Vision} & \textbf{Strengths} & \textbf{Weaknesses} \\
        \hline
        Transport &  &  &  &  &  &  &  \\
        \hline
        Submarine &  &  &  &  &  &  &  \\
        \hline
        Cruiser &  &  &  &  &  &  &  \\
        \hline
        Battleship &  &  &  &  &  &  &  \\
        \hline
    \end{tabular}
    \end{center}
\caption{Seat units and their properties}
\end{table}

\textbf{Additional restrictions}: Sea Transport units cannot attack at all and
Submarines can't stay more than three turns below the surface. However, when a
Submarine is below the surface it can't be targeted.\\

% Air: transport copter, battle copter, fighter, bomber

The following table shows every air unit name and its properties.\\

\begin{table}[H]
    \label{tab:air-units}
    \begin{center}
    \begin{tabular}{| l | m{1cm} | m{1.7cm} | m{1.0cm} | m{1.5cm} | m{1.1cm} | m{2.5cm} | m{2.5cm} |}
        \hline
        \textbf{Unit name} & \textbf{Cost} & \textbf{Movement} & \textbf{Power} & \textbf{Defense} & \textbf{Vision} & \textbf{Strengths} & \textbf{Weaknesses} \\
        \hline
        Transport copter &  &  &  &  &  &  &  \\
        \hline
        Battle copter &  &  &  &  &  &  &  \\
        \hline
        Fighter &  &  &  &  &  &  &  \\
        \hline
        Bomber &  &  &  &  &  &  &  \\
        \hline
    \end{tabular}
    \end{center}
\caption{Air units and their properties}
\end{table}

\textbf{Additional restrictions}: Transport copter can't attack other units.\\

\subsection{Buildings}

% Port, airport, barracks, city, operation center

Every building in \game\ will take one map tile and will act as the
\textit{building} terrain type. These are the available buildings in
the game along their properties:

\begin{table}[H]
    \label{tab:buildings}
    \begin{center}
    \begin{tabular}{| l | m{7cm}| m{3cm} | m{2.5cm} |}
        \hline
        \textbf{Building name} & \textbf{Description} & \textbf{Conquer points} & \textbf{Resources} \\
        \hline
        Operation center & Main building, if the enemy takes it, the player loses & 20 & 1500\\
        \hline
        City & no use & 10 & 1000 \\
        \hline
        Barracks & facility to gather land reinforcements & 10 & 1000 \\
        \hline
        Port & facility to gather sea reinforcements & 15 & 1000 \\
        \hline
        Airport & facility to gather air reinforcements & 15 & 1000 \\
        \hline
    \end{tabular}
    \end{center}
\caption{Building and their properties}
\end{table}

Conquer points represent the time a unit has to spend to take a building. If a
unit is at its full strength, it can conquer a 10 points building in one single
turn. Otherwise, the conquer will take more than one turn.\\

\subsection{Terrain}

% Grass, rock, snow, mountain, forest, jungle, river, road

Terrain affects unit movement, cover and vision range among other properties.
In \game\ there are different kinds of terrain which are described in the table
below.\\

\begin{table}[H]
    \label{tab:terrain}
    \begin{center}
    \begin{tabular}{| l | m{5cm} | m{5cm} |}
        \hline
        \textbf{Terrain type} & \textbf{Advantages} & \textbf{Disadvantages} \\
        \hline
        Grass & -& - \\
        \hline
        Rock & - & - \\
        \hline
        Snow & - & Movement loss \\
        \hline
        Mountain & Cover bonus, vision range bonus & Movement loss \\
        \hline
        Forest & Cover bonus & Movement loss \\
        \hline
        Jungle & Cover bonus & Movement loss \\
        \hline
        River & Cover loss & Movement loss \\
        \hline
        Road & Cover loss & Movement bonus \\
        \hline
        Building & Cover bonus & - \\
        \hline
    \end{tabular}
    \end{center}
\caption{Terrain types and their properties}
\end{table}


